Stateless Model Checking with Data-Race Preemption Points

### 2015-11-15 pldi-16/evaluation.tex
eval present dr-falsenegs result; not entirely happy with explanation

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{bargraph.pdf}
	\caption{{\bf TODO:} Is this graph productive to include in the paper? Or should I just leave the numbers in table format (the left half of Table~\ref{tab:drbugs})?}
	\label{fig:bargraph}
\end{figure}

@@

\subsection{Finding nondeterministic data-race candidates}
\label{sec:eval-falseneg}
Some memory accesses may be hidden in a control flow path that requires a nondeterministic preemption to be executed.
In such cases, a single-pass dynamic data-race detector
%could not achieve the coverage necessary
would fail
to identify a racing access pair as a candidate to begin with.
%
We counted how many such data-races, used as PPs, led to \quicksand~finding new bugs,
thereby making them {\em false negatives} of the single-pass approach.
We classified each data-race candidate according to whether \landslide~had reported them during the first interleaving, before any backtracking or preempting: if so, they were {\em deterministic data races} (hence could be found by single-pass).

To ensure a fair comparison, we disabled \landslide's {\em false-positive}-avoidance techniques during this experiment.
For example, we reported malloc-recycle data races during the first interleaving as {\em deterministic}, as a single-pass analysis must,
rather than waiting until future interleavings to confirm them (as explained in \sect{\ref{sec:recycle}}).

TODO: Present results.

At first, it might seem unfair to compare the data race bugs \quicksand~finds (10 CPU-hours)
against the candidates found by a prior work's single execution (less than a minute).
We argue this comparison is meaningful because prior work data-race tools %, being not integrated with a MC,
are not intended to discover new data race candidates under subsequent runs. %before discovering any initial candidates.
Running a data-race tool repeatedly for 10 CPU-hours could potentially uncover some of these false negatives at random,
but stress testing's comparative problem with achieving reliable coverage is already well-understood
\cite{chess-icb,gambit}.
This experiment also suggests that
other replay-based data-race tools \cite{racefuzzer,portend} should be configured to use the same sort of feedback loop as Iterative Deepening (\sect{\ref{sec:related-dr}}).
%i.e., discovering transitively-reachable data races while testing initial ones.
%although that would still not simultaneously be able to provide total verifications.
% TODO: read gambit paper

>>>>

%\begin{figure}[t]
%	\includegraphics[width=0.48\textwidth]{bargraph.pdf}
%	\caption{{\bf TODO:} Is this graph productive to include in the paper? Or should I just leave the numbers in table format (the left half of Table~\ref{tab:drbugs})?}
%	\label{fig:bargraph}
%\end{figure}

@@

\subsection{Finding nondeterministic data-race candidates}
\label{sec:eval-falseneg}
Some memory accesses may be hidden in a control flow path that requires a nondeterministic preemption to be executed.
In such cases, a single-pass dynamic data-race detector
%could not achieve the coverage necessary
would fail
to identify a racing access pair as a candidate to begin with.
%
We counted how many such data-races, used as PPs, led to \quicksand~finding new bugs,
thereby making them {\em false negatives} of the single-pass approach.
We classified each data-race candidate according to whether \landslide~reported them during the first interleaving,
before any backtracking or preempting:
if so, they were {\em single-pass data races}; otherwise, {\em nondeterministic}.

To ensure a fair comparison, we disabled \landslide's {\em false-positive}-avoidance techniques during this experiment.
For example, we reported malloc-recycle data races during the first interleaving, as a single-pass analysis must,
rather than waiting until future interleavings to witness them without the malloc-recycle pattern
(\sect{\ref{sec:recycle}}).

\begin{figure}[t]
	\includegraphics[width=0.48\textwidth]{nondet-drs-1-v2.pdf}
	\caption{Some data-race candidates may not be identified during a single program execution.
		Using nondeterministic data races as PPs,
		\quicksand~found 189\% as many bugs compared to the approach of prior work \cite{portend}.
	}
	\label{fig:dr-falsenegs}
\end{figure}
Figure~\ref{fig:dr-falsenegs} compares the types of data-race candidates necessary to expose each data-race bug in our test suite.
The first series represents the bugs found using PPs from single-pass data-race candidates,
% TODO: re read racefuzzer/portend paper to confirm this is true.
i.e., the state-of-the-art approach used by \cite{racefuzzer,portend}.
The second series shows all the data-race bugs \quicksand~found,
which includes the former type as well as new bugs involving nondeterministic data-races.
In total, among \quicksand's 68 total data-race bugs, just 36 could be found with single-pass data-race candidates alone.
%In total, we found 189\% as many bugs by using nondeterministic data-race candidates as PPs.

At first, it might seem unfair to compare the data race bugs \quicksand~finds (10 CPU-hours)
against the candidates found by a prior work's single execution (less than a minute).
We argue this comparison is meaningful because prior work data-race tools %, being not integrated with a MC,
are not intended to discover new candidates under subsequent runs. %before discovering any initial candidates.
Running a data-race tool repeatedly for 10 CPU-hours could potentially uncover some of these false negatives at random,
but stress testing's comparative problem with achieving reliable coverage is already well-understood
\cite{chess-icb,gambit}.
This result suggests that
other replay-based data-race tools \cite{racefuzzer,portend} should be configured to use a similar feedback loop as Iterative Deepening (\sect{\ref{sec:related-dr}}).
%i.e., discovering transitively-reachable data races while testing initial ones.
%although that would still not simultaneously be able to provide total verifications.
% TODO: read gambit paper
